The SMT Competition 2015--2018

### 2018-11-21 2018/report/SMT-COMP.tex
Minor

\begin{figure}
  \centering
  \begin{tikzpicture}
    \draw [gray] (0,0) -- (12,0);
    \draw [gray] (0,1.5) -- (12,1.5);
    \draw [gray] (0,3) -- (12,3);
    \draw [gray] (0,4.5) -- (12,4.5);
    \draw [gray] (0,6) -- (12,6);

@@

    \node [below] at (2,0) {\footnotesize 2015};
    \node [below] at (4.75,0) {\footnotesize 2016};
    \node [below] at (7.5,0) {\footnotesize 2017};
    \node [below] at (10.25,0) {\footnotesize 2018};
  \end{tikzpicture}
  \caption{Number of job pairs ($\blacksquare$) and total wall-clock time ($\square$).}
  \label{fig:job-pairs}
\end{figure}

@@

After 13 years, the SMT Competition is a well-established event that
garners wide interest from developers and users of SMT solvers.  The
competition continues to contribute to its original goals, including
adoption of the SMT-LIB format and sparking further advances in SMT,
and it provides a yardstick of performance for SMT solvers.

@@

Further development of the competition should be undertaken with care,
keeping in mind that any major changes require not just the
competition organizers, but also participants to adapt.  Immediate
action items for next year's organizers are
\begin{itemize}
\item the inclusion of {\tt check-sat} commands with unknown status in
  the application track; and
\item the definition of competition-wide rankings for the application
  and unsat-core track.
\end{itemize}

>>>>

\begin{figure}
  \centering
  \scalebox{.98}{\begin{tikzpicture}
    \draw [gray] (0,0) -- (12,0);
    \draw [gray] (0,1.5) -- (12,1.5);
    \draw [gray] (0,3) -- (12,3);
    \draw [gray] (0,4.5) -- (12,4.5);
    \draw [gray] (0,6) -- (12,6);

@@

    \node [below] at (2,0) {\footnotesize 2015};
    \node [below] at (4.75,0) {\footnotesize 2016};
    \node [below] at (7.5,0) {\footnotesize 2017};
    \node [below] at (10.25,0) {\footnotesize 2018};
  \end{tikzpicture}}
  \caption{Number of job pairs ($\blacksquare$) and total wall-clock time ($\square$).}
  \label{fig:job-pairs}
\end{figure}

@@

After 13 years, the SMT Competition is a well-established event that
garners wide interest from developers and users of SMT solvers.  The
competition continues to contribute to its original goals, including
adoption of the SMT-LIB format and sparking further advances in SMT,
and provides a yardstick of performance for SMT solvers.

@@

Further development of the competition should be undertaken with care,
keeping in mind that major changes require not just the competition
organizers, but also participants to adapt.  Immediate action items
for next year's organizers are
\begin{itemize}
\item the inclusion of {\tt check-sat} commands with unknown status in
  the application track; and
\item the definition of competition-wide rankings for the application
  and unsat-core track.
\end{itemize}
